Mega-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-08-28 analysis/Study1.qmd
renamed personality columns

df7a$STAIT_Mean <- df7a$STAIT_Sum/20

@@

```{r}
df9 <- read.csv("../data/VonMohr2023/DataSet_study3.csv")
df9 <- df9[complete.cases(select(df9, starts_with("IAS_"))), ]
df9 <- df9 |>
  mutate(Gender = as.character(ifelse(GENDER == "Man", "Male", ifelse(GENDER == "Woman", "Female", "Other")))) |>
  rename(
    Age=AGE, Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  ) |>
  mutate(
    BFI_NEUROTICISM = (BFI_1 + BFI_2 + BFI_3)/3,
    BFI_AGREEABLENESS = (BFI_10R + BFI_11 + BFI_12)/3,
    BFI_EXTROVERSION = (BFI_4 + BFI_5 + BFI_6),
    BFI_CONSCIENTIOUSNESS = (BFI_13 + BFI_14 + BFI_15R)/3,
    BFI_OPENNESS = (BFI_7 + BFI_8 + BFI_9)/3
    )
```

@@

```{r}
df10 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(
    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3,
    MAIA_EmoAwareness = MAIA_EmotionalAwareness, MAIA_AttentionReg = MAIA_AttentionRegulation,
    MAIA_SelfReg = MAIA_SelfRegulation,
  ) |>
  filter(!is.na(Urinate)) |> 
  datawizard::rescale(select=ias_vars, to = c(1, 5), range = c(0, 1)) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5))),
         across(starts_with("PI_"), \(x) datawizard::rescale(x, to = c(0, 1))),
         across(starts_with("Item_PHQ4_Depression_"), \(x) datawizard::rescale(x, to = c(1,4))),
        across(starts_with("Item_PHQ4_Anxiety_"), \(x) datawizard::rescale(x, to = c(1,4)))) |>
  mutate(PHQ4_Depression = Item_PHQ4_Depression_3 + Item_PHQ4_Depression_4,
          PHQ4_Anxiety = Item_PHQ4_Anxiety_1 + Item_PHQ4_Anxiety_2)
```

>>>>

df7a$STAIT_Mean <- df7a$STAIT_Sum/20
df7a$Neuroticism <- rowMeans(select(df7a,NEOFFI_01:NEOFFI_12))

@@

```{r}
df9 <- read.csv("../data/VonMohr2023/DataSet_study3.csv")
df9 <- df9[complete.cases(select(df9, starts_with("IAS_"))), ]
df9 <- df9 |>
  mutate(Gender = as.character(ifelse(GENDER == "Man", "Male", ifelse(GENDER == "Woman", "Female", "Other")))) |>
  rename(
    Age=AGE, Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  ) |>
  mutate(
    Neuroticism = (BFI_1 + BFI_2 + BFI_3)/3,
    Agreeableness = (BFI_10R + BFI_11 + BFI_12)/3,
    Extraversion = (BFI_4 + BFI_5 + BFI_6),
    Conscientiousness = (BFI_13 + BFI_14 + BFI_15R)/3,
    Openness = (BFI_7 + BFI_8 + BFI_9)/3) |>
  mutate(across(starts_with("BFI_"), \(x) datawizard::rescale(x, to = c(0, 1))))

@@

```{r}
df10 <- read.csv("https://raw.githubusercontent.com/RealityBending/IllusionGameReliability/main/data/preprocessed_questionnaires.csv") |>
  rename(
    Gender = Sex, Heart = Item_IAS_Interoception_1, Hungry = Item_IAS_Interoception_2,
    Breathing = Item_IAS_Interoception_3, Thirsty = Item_IAS_Interoception_4,
    Temp = Item_IAS_Interoception_5, Sex_arousal = Item_IAS_Interoception_6,
    Urinate = Item_IAS_Elimination_1, Defecate = Item_IAS_Elimination_2,
    Vomit = Item_IAS_Elimination_3, Wind = Item_IAS_Expulsion_1,
    Burp = Item_IAS_Expulsion_2, Sneeze = Item_IAS_Expulsion_3,
    Muscles = Item_IAS_Nociception_1, Bruise = Item_IAS_Nociception_2,
    Pain = Item_IAS_Nociception_3, Affective_touch = Item_IAS_Skin_1,
    Tickle = Item_IAS_Skin_2, Itch = Item_IAS_Skin_3,
    MAIA_EmoAwareness = MAIA_EmotionalAwareness, MAIA_AttentionReg = MAIA_AttentionRegulation,
    MAIA_SelfReg = MAIA_SelfRegulation,
  ) |>
  filter(!is.na(Urinate)) |> 
  datawizard::rescale(select=ias_vars, to = c(1, 5), range = c(0, 1)) |> 
  mutate(across(starts_with("MAIA_"), \(x) datawizard::rescale(x, to = c(0, 5))),
         across(starts_with("PI_"), \(x) datawizard::rescale(x, to = c(0, 1))),
         across(starts_with("Item_PHQ4_Depression_"), \(x) datawizard::rescale(x, to = c(1,4))),
        across(starts_with("Item_PHQ4_Anxiety_"), \(x) datawizard::rescale(x, to = c(1,4))),
        across(starts_with("IPIP6_"), \(x) datawizard::rescale(x, to = c(0,1))),
        PHQ4_Depression = Item_PHQ4_Depression_3 + Item_PHQ4_Depression_4,
          PHQ4_Anxiety = Item_PHQ4_Anxiety_1 + Item_PHQ4_Anxiety_2) |>
  rename(
     Agreeableness = IPIP6_Agreeableness,
    Conscientiousness = IPIP6_Conscientiousness,
    Extraversion = IPIP6_Extraversion,
    HonestyHumility = IPIP6_HonestyHumility,
    Neuroticism = IPIP6_Neuroticism,
    Openness = IPIP6_Openness
  )
```
